---
title: "Data Scientist Toolbox Course"
author: "Kishore Sathyanarayanan"
date: "Sunday, December 21, 2014"
output: html_document
runtime: shiny
---


#### What you can expect to see

=========================================

 * Identifying & downloading datafile from Web Source.
 * Reading the datafile for the Project.
 * Viewing Data & its Structures
 * Plotting Different graphs

=========================================

#### Software, Environment & Package Used

=========================================
 
 * R version 3.1.2 (2014-10-31) -- "Pumpkin Helmet"
 * Platform: x86_64-w64-mingw32/x64 (64-bit)
 * Packages
 
=========================================


Datafile sourced from "http://www.ats.ucla.edu/stat/stata/examples/" and created as 'Projdata.csv'


```{r echo = FALSE}
## getwd()
## list.files("Data")
a <- read.csv("Data/ProjData.csv")
```

Sample Header data from the datafile.
```{r echo = FALSE}

head(a)

```

Let's understand the Structure of the Data ...
```{r echo = FALSE}
str(a)
```

Column wise Min, Median, Mean & Max of the data...
```{r echo = FALSE}

## dim(a)

## a[1,"SNO"]
## a[1,"Gender"]
## a[2,"MeasureKGWeight"]
## a[2,"MeasureCMHeight"]
## is.matrix(a)

summary(a)
```

Weight Median Deviations between Measured vs Reported.
```{r echo = FALSE}
 median(a$MeasureKGWeight) - median(a$ReportedKGWeight)

```
Height Median Deviations between Measured vs Reported.
```{r echo = FALSE}
 median(a$MeasureCMHeight) - median(a$ReportedCMHeight)

```
Weight Mean Deviations between Measured vs Reported.
```{r echo = FALSE}
 mean(a$MeasureKGWeight) - mean(a$ReportedKGWeight)

```
Height Mean Deviations between Measured vs Reported.
```{r echo = FALSE}
 mean(a$MeasureCMHeight) - mean(a$ReportedCMHeight)
```

Having understood the data, lets see the plots now.
```{r echo = FALSE}

Gender <- table(a$Gender)
barplot(Gender, main="Gender Bar Chart",  xlab="Gender")

KGWt <- table(a$MeasureKGWeight)
barplot(KGWt, main="Weight Bar Chart",  xlab="Weight in KG")

CMHt <- table(a$MeasureCMHeight)
barplot(CMHt, main="Height Bar Chart",  xlab="Height in CM")

 Stk1 <- table(a$Gender , a$MeasureKGWeight)
 barplot(Stk1, main="Weight Distribution by Gender Bar Chart",
   xlab="Male Vs Female Weights ", col=c("darkblue","red"),
   legend = rownames(Stk1),beside = TRUE) 

Stk2 <- table(a$Gender , a$MeasureCMHeight)
 barplot(Stk2, main="Height Distribution by SNO Bar Chart",
   xlab="Male Vs Female Heights ", col=c("darkblue","red"),
   legend = rownames(Stk2),beside = TRUE) 


 plot(a$Gender,a$MeasureKGWeight, main="Weight Scatterplot", 
    xlab="Gender", ylab="Weight ", pch=10)

 plot(a$Gender,a$MeasureCMHeight, main="Height Scatterplot", 
    xlab="Gender", ylab="Height ", pch=10)


```

